---
title: "Fraud Detection"
author: "Manu Mathew"
date: "23 September 2019"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    code_folding: hide
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading packages and setting the path

```{r}
Install_And_Load <- function(packages) {
    k <- packages[!(packages %in% installed.packages()[,"Package"])];
    if(length(k))
    {install.packages(k, repos='https://cran.rstudio.com/');}
    
    for(package_name in packages)
    {suppressMessages(library(package_name,character.only=TRUE, quietly = TRUE));}
}

Install_And_Load(c("rapportools", 
                   "plyr" , "dplyr", "tidyr",
                   "plotly", "tictoc", 
                   "pracma", "tis",
                   "purrr", "purrrlyr",
                   "cluster", "Rtsne", "mlr",
                   "kknn", "glmnet", "h2o", "caret",
                   "irace"
                   ))

wd <- "E:/Documents/PersonalProjects/IEEE-CIS-Fraud_Detection/"

loadAndPlot <- function(variable, prefix, suffix = "_Plotly.rda") {
    ext <- paste0(variable, suffix)
    load(paste0(wd, "Data/Processed/Rdata/Plotly/", ext))
    p
}

```
# About Data

We have the following information from the official site and discussions on Kaggle competition page.


__Transaction Table__ 

* TransactionDT: timedelta from a given reference datetime (not an actual timestamp)
* TransactionAMT: transaction payment amount in USD
* ProductCD: product code, the product for each transaction
* card1 - card6: payment card information, such as card type, card category, issue bank, country, etc.
* addr: address
* dist: distance
* P_ and (R__) emaildomain: purchaser and recipient email domain
* C1-C14: counting, such as how many addresses are found to be associated with the payment card, etc. The actual meaning is masked.
* D1-D15: timedelta, such as days between previous transaction, etc.
* M1-M9: match, such as names on card and address, etc.
* Vxxx: Vesta engineered rich features, including ranking, counting, and other entity relations.

_Categorical Features:_

* ProductCD
* card1 - card6
* addr1, addr2
* Pemaildomain Remaildomain
* M1 - M9

__Identity Table__

Variables in this table are identity information – network connection information (IP, ISP, Proxy, etc) and digital signature (UA/browser/os/version, etc) associated with transactions.
They're collected by Vesta’s fraud protection system and digital security partners.
(The field names are masked and pairwise dictionary will not be provided for privacy protection and contract agreement)

_Categorical Features:_

* DeviceType
* DeviceInfo
* id12 - id38

# Data Ingestion

The train data is split into train_transaction (650 MB) and train_identity (25 MB) datasets. So lets have a look at the first few rows and after deciding on the data types, we shall read in the whole data. 


```{r eval=FALSE, include=FALSE}
sample_trainTransaction <- read.csv(file = paste0(wd, "Data/Processed/train_transaction.csv"),
                                    nrows = 10, 
                                    header = TRUE, 
                                    stringsAsFactors = TRUE)

trainTransaction <- read.csv(file = paste0(wd, "Data/Processed/train_transaction.csv"),
                                    # nrows = 10, 
                                    header = TRUE, 
                                    stringsAsFactors = TRUE)

save(trainTransaction,
     file = paste0(wd, "Data/Processed/Rdata/trainTransaction.rda"))

# str(sample_trainTransaction)
```

# Data manipulation

## trainTransaction
Convert these variables to factor-
* DeviceType
* DeviceInfo
* id12 - id38

```{r}

```

